%% Resume Template
%% @author: Suyash Gupta

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref} 


\usepackage{multicol}
\setlength{\columnsep}{1cm}
%\setlength{\tabcolsep}{25pt}

\usepackage[bottom=0.8in,top=0.9in]{geometry}
\geometry{a4paper}

\title{\vspace*{-2cm} \raggedright {\bf Suyash Gupta}}
\date{\vspace{-10ex}}	% removes date and its space

\makeatletter
\let\old@float\@float
\def\@float{\let\centering\relax\old@float}
\makeatother

\newcommand*\itbox{\makebox[10cm][l]}
 
\begin{document}
%\begin{multicols}{2}
%[


%\vspace*{-5pt}
%    {\let\newpage\relax\maketitle}

\maketitle
{\hspace{-0.9cm}
\begin{tabular}{ll}
Lab 2392, Academic Surge, University of California, Davis CA 95616 	& $\bullet$ \href{mailto:sugupta@ucdavis.edu}{sugupta@ucdavis.edu} \\ 
\url{gupta-suyash.github.io} & $\bullet$ Phone No:\\
Github: \url{https://github.com/gupta-suyash}  		& $\bullet$ Skype: gupta.suyash \\
\end{tabular}\newline
}
%]

\section*{EDUCATION}
{\setlength{\tabcolsep}{40pt}
\hspace{-1.5cm}
\begin{tabular}{ll}
{\bf University of California Davis} 		& Davis, CA 		\\
Doctor of Philosophy				& Jan 2018 -- present 	\\
(Transfer from Purdue)				&			\\
GPA: 4.00/4.00					&			\\
						&			\\
{\bf Purdue University} 			& West Lafayette, IN 	\\
Master of Science				& Aug 2015 -- Dec 2017 	\\
GPA: 3.83/4.00					&			\\
						&			\\
{\bf Indian Institute of Technology Madras}	& Chennai, India	\\
Master of Science (Research)			& Jan 2012 -- May 2015 	\\
GPA: 8.57/10.00					&			\\
						&			\\
{\bf GGSIP University}				& New Delhi, India	\\ 
Bachelor of Technology				& Aug 2007 -- May 2011	\\
GPA: 82.15/100					&			\\
\end{tabular}}



\section*{WORK EXPERIENCE}

\begin{itemize}
  \itemsep-0.2em
  \item \itbox{\bf Research Assistant, University of California, Davis} 	\itbox{Jan 2018 -- present}
  \begin{itemize}
    \vspace{-0.2cm}
    %\itemsep-0.5em
    \item Project – Efficient Agreement Protocols
    	\vspace{-0.1cm}
    	\begin{itemize}
    	  \itemsep-0.1em
    	  \item Design of two-phase non-blocking atomic commitment protocol.
    	  \item Design of topology-aware commitment protocol for geographically distant nodes.
    	\end{itemize}
    
    
    \item Project – Efficient Consensus Protocols and Resilient Architectures
    	\vspace{-0.1cm}
    	\begin{itemize}
    	  \itemsep-0.1em
    	  \item Design of a speculative two-phase byzantine fault-tolerant consensus protocol.
    	  \item Design of parallel and wait-free byzantine fault-tolerant consensus protocol. 
	  \item Design of global-scale byzantine fault-tolerant consensus protocol.
	  \item Design and analysis of high-throughput yielding permissioned blockchains.
	  \item Design of secure and fault-tolerant serverless architectures.
	  \item Design of efficient byzantine fault-tolerant consensus protocols using RDMA.
    	\end{itemize}
  \end{itemize}
  \item \itbox{\bf Research Intern, Novi (Libra/Facebook)} 			\itbox{June 2020 -- Sep 2020}
  \begin{itemize}
    \vspace{-0.2cm}
    %\itemsep-0.5em
    \item Automatic Profiling of Libra Framework
    	\vspace{-0.1cm}
    	\begin{itemize}
    	  \itemsep-0.1em
	  \item First work to automatically profile a blockchain system.
    	  \item Integrating Coz profiler [SOSP'15] with Libra framework.
	  \item Bug detection during Libra compile time.
    	\end{itemize}
    
    \item Analyzing Bottlenecks in Libra Framework
    	\vspace{-0.1cm}
    	\begin{itemize}
    	  \itemsep-0.1em
    	  \item Discovered performance bottlenecks in Libra's implementation of Patricia-Merkle Tries used to store user data.
	  \item Found optimal place to parallelize Libra VM and Executor.
	  \item Detected performance bottleneck in Libra VM's prologue. 
	  \item Trace analysis and annotation of Libra VM's load modules and resources.
    	\end{itemize}
  \end{itemize}

  \item \itbox{\bf Lead Architect, MokaBlox (Startup)} 				\itbox{Nov 2019 -- present}
  \begin{itemize}
    \vspace{-0.2cm}
    \item Design and Maintenance of ResilientDB Permissioned Blockchain Fabric.
  \end{itemize} 

  \item \itbox{\bf Teaching Assistant, Purdue University} 			\itbox{Aug 2017 -- Dec 2017}
  \item \itbox{\bf Research Assistant, Purdue University} 			\itbox{Aug 2015 -- Aug 2017}
  \begin{itemize}
    \vspace{-0.2cm}
    %\itemsep-0.5em
    \item Project – Probabilistic Test Data Generation
    	\vspace{-0.1cm}
    	\begin{itemize}
    	  \itemsep-0.1em
    	  \item Design of probabilistic test data generators that sample 
    	  	test inputs from various distributions such as Uniform, Binomial and Gaussian.
    	  \item Extension of probabilistic test data generators implementation to recursive types such as lists and trees.
    	\end{itemize}
    
    
    \item Project – Programming paradigms for distributed databases
    	\vspace{-0.1cm}
    	\begin{itemize}
    	  \itemsep-0.1em
    	  \item Development of a DSL in Ruby on Rails that implements users view of consistency.
    	  \item Implementation of a parser in Haskell that parses database SQL queries.
    	\end{itemize}
  \end{itemize}

  \item \itbox{\bf Intern, IBM India Research lab, New Delhi}			\itbox{Feb 2015 -- Apr 2015}
  \vspace{-0.6cm}
  \begin{itemize}
    \item Project -- Multithreaded Analysis of Java Programs
	\vspace{-0.2cm}
	\begin{itemize}
	  \itemsep-0.2em
	  \item Study of a novel parallel escape analysis and pointer analysis algorithm.
	  \item Testing of a novel Java decompilation strategy.
	  \item Analysis of a novel Slicing algorithm.	
	\end{itemize}
  \end{itemize}

  \item \itbox{\bf Project Associate, IIT Madras}			\itbox{Jan 2014 -- Dec 2014}
  \vspace{-0.6cm}
  \begin{itemize}
    \item Project – Optimizing parallel programs for multicore systems.
	\vspace{-0.1cm}
	\begin{itemize}
	  \itemsep-0.1em
	  \item Design of two novel task parallel optimizations for reduction of
	  	task creation and task termination operations.
	  \item Implementation of the two novel optimizations in X10 compiler.
	  \item Analyzing the impact of proposed optimizations on the energy consumption.
	\end{itemize}
  \end{itemize}

  \item \itbox{\bf Teaching Assistant, IIT Madras}			\itbox{Jan 2012 –- Dec 2013}

  \item \itbox{\bf Intern, Bharat Heavy Electical Limited}		\itbox{Jun 2010 – July 2010}


\end{itemize}



\section*{PUBLICATIONS}
\subsection*{Books}
\begin{itemize}
\itemsep-0.2em

\item {\bf S. Gupta}, J. Hellings and M. Sadoghi, {\em Fault-tolerant Distributed Transactions on Blockchain}, Morgan $\&$ Claypool Synthesis Lectures on Data Management (to appear), 2020.

\end{itemize}


\subsection*{Conferences}
\begin{itemize}
\itemsep-0.2em

\item {\bf S. Gupta}, J. Hellings and M. Sadoghi, {\em RCC: Resilient Concurrent Consensus for High-Throughput Secure Transaction Processing}, To appear in 37th IEEE International Conference on Data Engineering (ICDE). 2021.

\item {\bf S. Gupta}, S. Rahnama and M. Sadoghi, {\em Permissioned Blockchain Through the Looking Glass: Architectural and Implementation Lessons Learned}, In 40th IEEE International Conference on Distributed Computing Systems (ICDCS). 2020.

\item {\bf S. Gupta}, S. Rahnama, J. Hellings and M. Sadoghi, {\em ResilientDB: Global Scale Resilient Blockchain Fabric}, In 46th International Conference on Very Large Databases (VLDB). 2020 --- {\bf \em Artifact Evaluated}.

\item T. Qadah, {\bf S. Gupta} and M. Sadoghi, {\em Q-Store: Distributed, Multi-partition Transactions via Queue-oriented Execution and Communication}. In 23rd International Conference of Extending Database Technology (EDBT), 2020.

\item {\bf S. Gupta}, J. Hellings and M. Sadoghi, {\em Brief Announcement: Revisiting Consensus Protocols through Wait-free Parallelization}, In 33rd International Symposium on Distributed Computing (DISC). 2019.

\item {\bf S. Gupta} and M. Sadoghi, {\em EasyCommit: A Non-blocking Two-phase Commit Protocol}, In 21st International Conference of Extending Database Technology (EDBT), 2018.

\item {\bf S. Gupta}, R. Shrivastava, and V. K. Nandivada, {\em Optimizing Recursive Task Parallel Programs}, In 31st International Conference on Supercomputing (ICS), 2017.
\end{itemize}


\subsection*{Journals}
\begin{itemize}
\itemsep-0.2em

\item {\bf S. Gupta} and M. Sadoghi, {\em Efficient and non-blocking agreement protocols}, Distributed and Parallel Database (DAPD), 2019.

\item {\bf S. Gupta} and V. K. Nandivada, {\em IMSuite: A Benchmark Suite for Simulating Distributed Algorithms}, Journal of Parallel and Distributed Computing (JPDC), Elsevier, 2015.
\end{itemize}

\subsection*{Selected Articles}
\begin{itemize}
\itemsep-0.2em

\item {\bf S. Gupta}, {\em Resilient and Scalable Architecture for Permissioned Blockchain Fabrics}, PhD Workshop, 
In 46th International Conference on Very Large Databases (VLDB), 2020.

\item {\bf S. Gupta}, J. Hellings, T. Qadah, S. Rahnama and M. Sadoghi, {\em Efficient Transaction Processing in Byzantine Fault Tolerant Environments}, In International Workshop on High Performance Transaction Systems (HPTS), 2019 -- A Biennial Workshop.

\item {\bf S. Gupta} and M. Sadoghi, {\em Blockchain Transaction Processing}, In Encyclopedia of Big Data Technologies. Springer, Cham, 2018.
\end{itemize}


\subsection*{Tutorials}
\begin{itemize}
\itemsep-0.2em

\item {\bf S. Gupta}, J. Hellings, S. Rahnama and M. Sadoghi,{\em Building High Throughput Permissioned Blockchain Fabrics: Challenges and Opportunities}, In 46th International Conference on Very Large Databases (VLDB), 2020.

\item {\bf S. Gupta}, J. Hellings, S. Rahnama and M. Sadoghi, {\em Blockchain consensus unraveled: Virtues and Limitations}, In 14th ACM International Conference on Distributed and Event-Based Systems (DEBS), 2020.

\item {\bf S. Gupta}, J. Hellings, S. Rahnama and M. Sadoghi, {\em An In-Depth Look of BFT Consensus in Blockchain: Challenges and Opportunities}, Middleware Tutorials, 2019.
\end{itemize}


\subsection*{Demonstrations}
\begin{itemize}
\itemsep-0.2em

\item S. Rahnama, {\bf S. Gupta}, T. Qadah, J. Hellings and M. Sadoghi, {\em Scalable, Resilient and Configurable Permissioned Blockchain Fabric}, In 46th International Conference on Very Large Databases (VLDB), 2020.

\end{itemize}

\subsection*{Pre-Prints (Under Submission)}
\begin{itemize}
\itemsep-0.2em
\item {\bf S. Gupta}, J. Hellings and M. Sadoghi, {\em Proof-of-Execution: Reaching Consensus through Fault-Tolerant Speculation}, available on Arxiv, 2019.
\end{itemize}


\section*{OTHER RESOURCES}
\begin{itemize}
\itemsep-0.2em

\item ResilientDB Fabric, available online at \url{https://resilientdb.com/}. Source code is available at \url{https://github.com/resilientdb/resilientdb} and has been forked/starred more than $60$ times.

\item IMSuite benchmark, available online at \url{http://www.cse.iitm.ac.in/~krishna/imsuite} and has been downloaded over $5000$ times and well-cited.

\item DistCheck, a Litmus Testing tool, available online at \url{https://github.com/gupta-suyash/DistCheck}.

\end{itemize}



\section*{AWARDS \& HONORS}
\begin{itemize}
\itemsep-0.2em
\item Student Grant from VLDB Endowment for participation in VLDB 2020.
\item Student Travel Grants from Middleware 2019.
\item GGCS Travel Award 2019 from UC Davis to attend HPTS 2019.
\item Scholarship to attend VMW/CAV 2017 at Heidelberg, Germany, 23 -- 28 July 2017.
\item Travel grant to present work at ICS 2017 at Chicago, IL, 14 -- 16th June 2017. 
\item Attended OPLSS'16 at Eugene, OR, 19th June 2016 – 2nd July 2016.
\item Best Use of Data Visualization, Best Mobile App, Most Launchable product sponsored by Dorm Room Fund and PrincetonPy/PICSciE Prize at HackPrinceton 2016.
\item First Prize at HackIllinois 2016 (Best Software Hack), and 
Best use of Microsoft Technology award – 19-21st February 2016.
\item First at Purdue University and finalist entry to Windward Code Wars Spring 2016.
\item Qualified for Semi-finals at Microsoft Imagine Cup Spring 2016.
\item First Prize at Boston Hacks 2015 – 31st Oct – 1st Nov 2015.
\item Scholarship to attend POPL/PLMW, at Munbai, India, 12 -- 18 Jan 2015.
\item Outstanding Teaching Assistant Award for courses: CS3310 (Aug 12), CS6848 (Jan 13).
\item Scholarship from MHRD, Government of India, for qualifying All India Graduate
Aptitude Test in Engineering (GATE) and securing admission at IIT Madras.
\item 1st prize, Inter College project competition, 2011, organized by GGSIPU and Delhi
Knowledge Development Foundation
\item 2nd prize, Technical Paper Presentation, 2011, organized in association of Computer
Society of India (CSI) at Jamia Millia Islamia.
\item 2nd prize at C/C++ programming at Info Expression 2009.
\end{itemize}



%
%
%\section*{SKILLS}
%\begin{tabular}{ll}
%Languages:	&	 C, C++, Java, OCaml, Clojure, Haskell, Ruby, X10, Cilk, Rails, Python	\\
%Web Technology:	&	 HTML, CSS, PHP								\\
%Database:	&	 Mysql, PostgreSQL, Sequel, Oracle 9i					\\
%Worked on:	&	 8086, 8051, Arm Cortex A8, Beagle Board				\\
%\end{tabular}


%\section*{ACADEMIC PROJECTS}
%\begin{itemize}
%\itemsep-0.2em
%\item \itbox{Development of Three Phase Commit Protocol:} 		\itbox{Feb –- Apr 2016}
%\item \itbox{Extension of XINU Operating System:} 			\itbox{Aug –- Dec 2015}
%\item \itbox{Development of Parallel Pagerank algorithm using techniques}
%\item[] \itbox{such as Matrix-Vector multiplication and Random Walk:}	\itbox{Aug –- Dec 2015}
%\item \itbox{Implementation of Feedback-Directed Prefetcher:} 		\itbox{Aug –- Nov 2012}		
%\item \itbox{Design of Mini-java compiler:} 				\itbox{Aug –- Nov 2012}		
%\item \itbox{Design of Super scalar processor using VHDL:} 		\itbox{Jan –- Apr 2012}		
%\item \itbox{Reaching Agreement in Network with Curious Nodes:} 	\itbox{Jan –- Apr 2012}
%\item \itbox{Design of Micro-java Interpreter:}	 			\itbox{Jan –- Apr 2012}
%\end{itemize}


\section*{SEMINARS / TALKS}
\begin{itemize}
\itemsep-0.2em
\item {\em RCC: Resilient Concurrent Consensus for High-Throughput Secure Transaction Processing} at Novi Intern Seminars on 08/17/2020.
\item {\em ResilientDB: Global Scale Resilient Blockchain Fabric} at VLDB'20 on 09/01/2020 and 09/03/2020 (recorded video).
\item {\em Building High Throughput Permissioned Blockchain Fabrics: Challenges and Opportunities} at VLDB'20 on 09/01/2020 (recorded video).
\item {\em Resilient and Scalable Architecture for Permissioned Blockchain Fabrics} at PhD Workshop, VLDB'20 on 08/31/2020 (recorded video).
\item {\em Blockchain consensus unraveled: Virtues and Limitations} at DEBS'20 on 07/14/2020.
\item {\em An In-Depth Look of BFT Consensus in Blockchain: Challenges and Opportunities} at REIMAGINE v1.0 on 12/10/2019.
\item {\em ResilientDB: Global Scale Resilient Blockchain Fabric} at FAB'20 on 05/01/2020 (recorded video).
\item {\em Permissioned Blockchain Through the Looking Glass: Architectural and Implementation Lessons Learned} at FAB'20 on 05/01/2020 (recorded video).
\item {\em An In-Depth Look of BFT Consensus in Blockchain: Challenges and Opportunities} at Middleware on 12/10/2019.
\item {\em EasyCommit: A non-blocking two-phase commit protocol} at EDBT'18 on 03/29/2018.
\item {\em Optimizing recursive task parallel programs} at ICS'17 on 06/14/2017.
\item {\em IMSuite: A benchmark suite for simulating distributed algorithms} at Purdue University on 09/15/2016.
\item {\em Analyzing Recursive Task Parallel Programs} at Indian Institute of Technology Madras on 10/16/2014.
\end{itemize}


\section*{SERVICES}
\begin{itemize}
\itemsep-0.2em
\item Reviewer, ICDCS 2021
\item pVLDB Reproducibility 2019 -- present
\item Reviewer, SIGMOD Record 2019
\item Web Chair, Middleware 2019.
\item Volunteer, VLDB 2019.
\item External Reviewer, EDBT 2018.
\item External Reviewer, Middleware 2018.
\end{itemize}


\section*{MENTORING}
\begin{itemize}
\itemsep-0.2em
\item Alex Su, B.Sc, UC Davis (Summer 2020 - ongoing)
	\begin{itemize}\vspace{-2mm}
	\item Project: Byzantine Resilient Serverless Framework.
	\end{itemize}
\item Shubham Pandey, MS, UC Davis (Summer 2020 - ongoing)
	\begin{itemize}\vspace{-2mm}
	\item Project: Efficient Byzantine Consensus using RDMA.
	\end{itemize}
\item Erik Linsenmayer, B.Sc, UC Davis (Spring 2020 - ongoing)
	\begin{itemize}\vspace{-2mm}
	\item Project: Byzantine Resilient Serverless Framework.
	\end{itemize}
\item Rohan Sogani, MS, UC Davis (Winter 2020 - ongoing)
	\begin{itemize}\vspace{-2mm}
	\item Project: Efficient Byzantine Fault-Tolerant consensus through Sharding.
	\end{itemize}
\item Priya Holani, MS, UC Davis (Winter 2020 - Summer 2020)
	\begin{itemize}\vspace{-2mm}
	\item Project: Efficient Byzantine Fault-Tolerant consensus through Sharding.
	\end{itemize}
\item Dhruv Krishnan, MS, UC Davis (Winter 2020 - Summer 2020)
	\begin{itemize}\vspace{-2mm}
	\item Project: Efficient Byzantine Fault-Tolerant consensus through Sharding.
	\end{itemize}
\item Xinyuan Sun, B.Sc, UC Davis (Winter 2020 - Summer 2020)
	\begin{itemize}\vspace{-2mm}
	\item Project: Efficient Byzantine Consensus using RDMA.
	\end{itemize}
\item Federico Mengozzi, B.Sc, UC Davis (Fall 2018 - Fall 2019) -- Now at Carsbarter, Murcia 
	\begin{itemize}\vspace{-2mm}
	\item Project: Smart Contracts support in ResilientDB.
	\end{itemize}
\item Shreenath Iyer, MS, UC Davis (2018-2019) -- Now at Amazon, Seattle 
	\begin{itemize}\vspace{-2mm}
	\item Project: Data Visualization Support for ResilientDB Fabric.
	\end{itemize}
\item Romen Rubero, B.Sc, UC Davis (Fall 2018 - Spring 2019) -- Now at Carsbarter, Murcia
	\begin{itemize}\vspace{-2mm}
	\item Project: Crypto Profiling/Benchmarking in ResilientDB Fabric.
	\end{itemize}
\item Patrick J. Liao, B.Sc, UC Davis (Winter 2018 - Fall 2018) -- Now at Juniper Technology, Bay Area 
	\begin{itemize}\vspace{-2mm}
	\item Project: Robust Byzantine Fault-Tolerant Protocols in ResilientDB.
	\end{itemize}
\item Domenic Cianfichi, MS, UC Davis (Winter 2018 - Summer 2018)
	\begin{itemize}\vspace{-2mm}
	\item Project: Fault-tolerant Consensus Protocols in ResilientDB.
	\end{itemize}
\end{itemize}

\end{document}
